Coupled response of stomatal and mesophyll conductance to light enhances photosynthesis of shade leaves under sunflecks

### 2016-07-13 gm_pce/manuscript_gmes.Rmd
pce edits

---
title: Coupled response of stomatal and mesophyll conductance to light enhances photosynthesis of shade leaves under sunflecks
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: plant-cell-environment.csl
bibliography: references.bib
---

>>>>

---
title: Coupled response of stomatal and mesophyll conductance to light enhances photosynthesis of shade leaves under sunflecks
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_pce.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: plant-cell-environment.csl
bibliography: references.bib
---
